% some change in dev/epfl

%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11.5pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[blue]{casual}                % idem
\moderncvtheme[green]{classic}
% character encoding
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{hyperref}

\AtBeginDocument{\hypersetup{pdfborder = 0 0 1,linkcolor=blue}}
% adjust the page margins
\usepackage[scale=0.855]{geometry}
\setlength{\hintscolumnwidth}{1.9cm}
%\usepackage{multibib}
\recomputelengths    % required when changes are made to page layout lengths
%\newcites{conf}{Conference}
% personal data
\firstname{Naveen}
\familyname{Kuppuswamy}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\extrainfo{Postdoctoral Fellow, iCub Facility,\\Istituto Italiano di Tecnologia} % optional, remove the line if not wanted
%\address{\hspace{-1in}Corso Paganini 33}{Genova, 16125}    % optional, remove the line if not wanted
\mobile{mobile (+39)3914659316}                    % optional, remove the line if not wanted
% \phone{(312) 413-8265}                      % optional, remove the line if not wanted
% \fax{312 996 1491}                          % optional, remove the line if not wanted
\email{naveen.kuppuswamy@iit.it}                      % optional, remove the line if not wanted
\homepage{naveenoid.wordpress.com}
%\homepage{\href{http://www.ifi.uzh.ch/ailab/group/pfeifergroup/naveenkuppuswamy.html}{link}}

%\photo[60pt]{naveen_dwengo}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"No man should escape our universities without knowing how little he knows." -- J. Robert Oppenheimer}                 % optional, remove the line if not wanted
\quote{Research Interests : state estimation, robot and human dynamics, robot locomotion, bio-inspired control, and model/control order reduction}  
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
% 
% \usepackage[nonewsec]{splitbib}
% 
% \makeatother
% \SBtitlestyle{simple}
% 
% \begin{category}[J]{Journals and Book Chapters}
% \SBentries{Kim2008,Kuppuswamy2013b,Kuppuswamy2013c,Kuppuswamy2013d,Kuppuswamy2013e,Kuppuswamy2013f,Marques2013}
% \end{category}
% 
% \begin{category}[C]{Conferences}
% \SBentries{Kim2007,Kuppuswamy2013a,Kuppuswamy2012a,Marques2012a,Nakajima2011,Stonier2007,Yoo2006}
% \end{category}
% 
% \begin{category}[P]{Posters}
% \SBentries{Kuppuswamy2011a,Kuppuswamy2011b}
% \end{category}

\usepackage{multibib}
\newcites{journals}{Journals and Book Chapters}
\newcites{underprep}{Journals under preparation}
\newcites{conferences}{Conferences}
\newcites{posters}{Workshops and Posters}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%  \nocitejournals{Kim2008,Kuppuswamy2014a}
%  \nociteconferences{Kim2007,Kuppuswamy2014b,Kuppuswamy2012a,Kuppuswamy2013a,Marques2012a,Nakajima2011,Stonier2007,Yoo2006,Eljaik2015a,Nori2015,Kuppuswamy2006,Kuppuswamy2006b, Nakajima2011b,Shin2008,Carbajal2010}
%  \nociteposters{Kuppuswamy2011a,Kuppuswamy2011b,Eljaik2015b,Latella2015,Latella2015b,Kuppuswamy2015,Nakajima2011c,Kuppuswamy2012b}
 \nocitejournals{Kuppuswamy2014a,Kim2008}
 \nociteconferences{Latella2015c,Eljaik2015a,Nori2015,Kuppuswamy2014b,Kuppuswamy2013a,Kuppuswamy2012a,Marques2012a,Nakajima2011,Nakajima2011b,Carbajal2010,Shin2008,Kim2007,Stonier2007,Yoo2006,Kuppuswamy2006,Kuppuswamy2006b}
 \nociteunderprep{Kuppuswamy2016a, Romano2016a}%, Kuppuswamy2016b}
 \nociteposters{Kuppuswamy2011a,Kuppuswamy2011b,Eljaik2015b,Latella2015,Latella2015b,Kuppuswamy2015,Kuppuswamy2012b,Traversaro2015a}
%\nociteposters{Kuppuswamy2011a,Kuppuswamy2011b,Eljaik2015b,Latella2015,Latella2015b,Kuppuswamy2015,Nakajima2011c,Kuppuswamy2012b,Traversaro2015a}

\maketitle
%Research Interests : reduced dimensional motor control, developmental robotics, biorobotics

\section{Education}
\cventry{2009-2014}{PhD in Artificial Intelligence}{Dept. of Informatics}{University of Z\"{u}rich}{Switzerland}{\small
\textbf{Thesis } : \emph{Exploiting reduced dimensionality in the design and control of embodied systems}\\
\textbf{Supervisor} : Prof. Dr. Rolf Pfeifer\\
\textbf{Marie Curie Fellow}
}
\cventry{2005--2007}{MS in Electrical Engineering and Computer Science}{Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, South Korea}{}{\small 
\textbf{Thesis} : \emph{Nonlinear inverse dynamic control of an omnidirectional mobile robot using slip rolling modes}\\
\textbf{Supervisor} : Prof. Dr. Jong-Hwan Kim\\
\textbf{Korean Research Foundation (KRF) Scholar}
}
\cventry{2001-2005}{BE in Instrumentation and Control Engineering}{SRM Engineering College, Anna University}{Chennai, India}{}{}  % arguments 
\vfill
\section{Experience}
\subsection{Academia}
% \cventry{2014--now}{EU Projects KOROIBOT(IP), CoDyCo(IP)}{RBCS}{IIT}{Italy}{\small Working on state estimation and lasrge-scale sensor fusion for dynamic walking on humanoids.}
% \cventry{2009--2013}{EU Projects OCTOPUS(IP), ROBOTDoC(ITN), AMARSi(IP)}{AI Lab}{UZH}{Switzerland}{\small Worked on reduced dimensional control, learning of motor primitives (AMARSi and ROBOTDoC), continuum robot control and low-level control hardware development (OCTOPUS). The research for project ROBOTDoC was partially carried out at the Centre for Robotics and Neural Systems, Plymouth University, UK.}
% \cventry{2005--2007}{Information Technology Research Center (ITRC) Funded Projects}{Robot Intelligence Technology Lab}{KAIST}{Daejeon, South Korea}{\small Worked on the development and control of an omnidirectional football robot; on movement planning and control of bipedal robots; and on ubiquitous robots and cognitive control architectures with episodic memory.}
\cventry{2014--now}{Postdoctoral Fellow}{Dynamic Interaction Control Lab, iCub Facility}{IIT}{Italy}{\small Whole-body state estimation and large-scale sensor fusion for articulated rigid bodies (humanoid robots); human dynamics estimation using motion capture and wearable systems (EU Projects \emph{KOROIBOT}, and \emph{CoDyCo}).}% Recipient of the Swiss \textbf{NCCR-Robotics Postdoc Exchange Fellowship} for 2016 (to be carried out at the Biorobotics Lab, EPFL, Lausanne). }
\cventry{2009--2014}{Doctoral Student}{Artificial Intelligence (A.I) Lab}{UZH}{Z\"{u}rich,Switzerland}{\small Reduced dimensional control, learning of motor primitives (EU Projects \emph{AMARSi} and \emph{ROBOTDoC}), continuum robot control and embedded control hardware development (EU Project \emph{OCTOPUS}).}
\cventry{2012}{Visiting Researcher}{Center for Robotics and Neural Systems (CRNS)}{Plymouth University}{Plymouth, UK}{\small Muscle synergies, motor control and reduced dimensionality (ROBOTDoC).}
\cventry{2005--2007}{Research Assistant}{Robot Intelligence Technology (RIT) Lab}{KAIST}{Daejeon, South Korea}{\small Development and control of an omnidirectional football robot; movement planning and control of bipedal robots; ubiquitous robots and cognitive control architectures with episodic memory.}
% ----------------------------
\vfill
\subsection{Industry}
\cventry{2007--2008}{Engineer R\&D}{Yujin Robot Co. Ltd.}{Seoul}{South Korea}{Service robot middleware and computer vision for human robot interaction (iRobiQ edutainment robot).}                % arguments 3 to 6 are optional
\vfill
\subsection{Non-Profit}
\cventry{2013--now}{Engagement Manager}{Dwengo pzw}{Ghent}{Belgium}{Non-profit taking robotics and micro-controller programming to under-privileged children. Coordinated and executed the project in Chennai, India. Non-profit was a \textbf{Google RiSE 2014} grant award winner.
}

\newpage
\section{Academic Activities}
%\subsection{Publications}
%\cvlistitem{\small Coauthored $3$ journal papers ($1$ published and $2$ to be submitted shortly), $1$ book chapter, $16$ conference papers, and $9$ workshops/posters.}% Full published list available at \href{http://scholar.google.ch/citations?user=Ec3-TsUAAAAJ}{Google Scholar}}.
\subsection{Teaching Assistance and Student Supervision}
\cvlistitem{\small Supervised $2$ bachelor's and  $2$ master's theses, and $5$ semester projects.}
%Tripti, Matt, Philip, Umar, Vivienne, Sant, Aditya, Mirium 
\cvlistitem{\small Introduction to AI (Fall 2010, Fall 2011), Formal Methods in Computer Science II (Fall 2009, Fall 2012), Bio-Inspired Robotics (Spring 2009). Multiple invited guest lectures on an \emph{Introduction to Reservoir Computing}.}
\vfill
\subsection{Summer Schools / Technical Training}
%\cvlistitem{\small EMBODYi Projects Summer School on Embodied Intelligence, Livorno, Italy (September 2010).}
\cvlistitem{\small Veni Vidi Vici (iCub robot summer school), Sestri Levante, Italy (August 2011, July 2014).}
\cvlistitem{\small Summer School on Impedance Control, Fraueninsel Chiemsee, Germany (July 2011).}
\cvlistitem{\small Multiple training activities in the RobotDoc network (September 2009 - August 2013)}
\vfill
\subsection{Grant Awards / Fellowships}
\cvlistitem{\small NCCR Robotics Postdoc Exchange Fellowship (2016)}
\cvlistitem{\small Google RISE Award, for Dwengo Activities (2014)}
\cvlistitem{\small Marie Curie Fellowship (2011-2014)}
\cvlistitem{\small Korean Research Foundation Scholarship (2005-2007)}
\vfill
\subsection{Article Reviews}
\cvlistitem{\small \textbf{Journals} : IEEE Transactions on Robotics, IEEE Transactions on Industrial Electronics, and Frontiers in Bioengineering.}
\cvlistitem{\small \textbf{Conferences} : IEEE RSJ International Conference on Intelligent Robots and Systems (IROS), and IEEE RAS International Conference on Humanoid Robots.}
\vfill
\subsection{Invited Talks and Seminars}
\cvlistitem{\small Indian Institute of Science, Centre for Nano Science and Engg., Bangalore, India (May 2015)}
\cvlistitem{\small Max Planck Institute for Intelligent Systems, Autonomous Motion Department, T\"{u}bingen, Germany (January 2015)}
\cvlistitem{\small Technical University of Darmstadt, Locomotion Laboratory, Darmstadt, Germany (January 2015)}
\cvlistitem{\small University of Hamburg, Dept. of Computer Science, Hamburg, Germany (January 2015)}
\cvlistitem{\small Bielefeld University, Center of Excellence - Cognitive Interaction Technology CITEC, Bielefeld, Germany (January 2015)}
\cvlistitem{\small EPFL, Biorobotics Lab, Lausanne, Switzerland (November 2014)}
\cvlistitem{\small Osaka University, Hosoda Laboratory, Osaka, Japan (May 2014)}
\cvlistitem{\small Zurich University of the Arts (ZHdK), Dept. of Interaction Design, Z\"{u}rich, Switzerland (January 2014)}
\cvlistitem{\small Plymouth University, Center for Robotics and Neural Systems, Plymouth, UK (May 2013)}

\vfill
\section{Professional Activities and Other Achievements} 
% \cvlistitem{\small \textbf{Engagement Manager} at Dwengo pzw, a non-profit focusing on taking robotics and micro-controllers to underprivileged children. }
\cvlistitem{\small \textbf{Chairman} at the \emph{Science Cafè} at the \emph{Robots on Tour} event, Cafè Sphères, Z\"{u}rich, on $8^{th}$ March, 2013. }
\cvlistitem{\small \textbf{Coordinator} of the brown bag lecture series conducted at the AI Lab and at ETH Zurich from 2009 until 2014.}
\cvlistitem{\small \textbf{Publicity Chair} at the \emph{Postgraduate Conference on Robotics and Development of Cognition (ROBOTDoC-PhD)}, a satellite event of the International Conference on Artificial Neural Networks (ICANN 2012), at the University of Lausanne, Switzerland, on $10-12^{th}$ September 2012.}
\vfill
\subsection{Awards} 
\cvlistitem{\small \textbf{Best Paper Award}, \emph{$2^{nd}$ International Electronic Conference on Sensors and Applications}, December 2015 (For the paper Latella et al, 2015).}

\cvlistitem{\small \textbf{Best Documentation Award}, \emph{$13^{th}$ International Micro-robot Maze Contest}, held in Nagoya, Japan in October 2004.}
% \vfill
% \subsection{Open Source Contributions} 
% \cvlistitem{\small Contributed to several open source projects such as yarp, iCub, iDynTree, wholeBodyInterface etc. (complete list of recent contributions available at \href{https://github.com/naveenoid}{github}).}




% \item 
% \textbf{Dr. Francesco Nori}{\small\\Team Leader, Cognitive Humanoids Lab,\\ Department of Robotics, Brain and Cognitive Sciences (RBCS), \\Istituto Italiano di Tecnologia, Genova.\\ Email : \href{mailto:francesco.nori@iit.it}{francesco.nori@iit.it}}
% \item 
% \textbf{Prof. Giulio Sandini}{\small\\Director,\\ Department of Robotics, Brain and Cognitive Sciences (RBCS), \\Istituto Italiano di Tecnologia, Genova.\\ Email : \href{mailto:giulio.sandini@iit.it}{giulio.sandini@iit.it}}
% \item 
% % \textbf{Prof. Dr. Chris  Harris}{\small \\ Professor of Neuroscience, Centre for Robotics and Neural Systems (CRNS)\\Plymouth University, United Kingdom.\\ Email : \href{mailto:chris.harris@plymouth.ac.uk}{chris.harris@plymouth.ac.uk}}
% \textbf{Prof. Dr. Rolf Pfeifer}{\small \\ Retired Professor of Computer Science, Institute for Informatics (IFI)\\University of Z\"{u}rich, Switzerland.\\ Email : \href{mailto:rolf.pfeifer@ifi.uzh.ch}{rolf.pfeifer@ifi.uzh.ch}}
% % \end{minipage}
% \end{enumerate}
\newpage
\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\nocite{*}

%\nocite{Kuppuswamy2012a}

%\nocite{Kuppuswamy2013a}
\renewcommand{\refname}{Publications}
\section*{Publications}

\bibliographystyle{plainyrrev}
\bibliographystylejournals{plainyrrev} 
\bibliographyjournals{naveenPubs} \vfill
\bibliographystyleunderprep{plainyrrev} 
\bibliographyunderprep{naveenPubs} \vfill
\bibliographystyleconferences{plainyrrev}
\bibliographyconferences{naveenPubs}\vfill
\bibliographystyleposters{plainyrrev}
\bibliographyposters{naveenPubs} 
\newpage

\section*{Outreach and Public Media}
\cvlistitem{\small Multiple interviews in South Indian regional newspapers regarding \emph{Dwengo} project activities.}
\cvlistitem{\small Rai TV, interview by the Italian language TV channel on the robotics research conducted at IIT; featured a brief personal interview, February 2015.} 
\cvlistitem{\small Cronaca Livorno, interview by the Italian language newspaper on AI Lab and my participation in the Octopus Project and the FET EMBODYi Summer School, September 2010.}
\cvlistitem{\small Wired Magazine, \emph{Seoul of a new machine}; an article on the research of the RIT group, KAIST and me on the ubiquitous robot project,  December 2006.}
\cvlistitem{\small Sun TV Network, Interview by the Tamil language TV channel on our microrobot project and the International Microrobot Maze Contest,  December 2004.}

%\vspace{.4in}
\section{Technical Skills} 
\cvline{Languages}{\small C++, C, MATLAB Script, Python, \LaTeX, Java, HTML}%{ }{ }%{Software Platforms}{MATLAB, SolidMaple, }
\cvline{Embedded}{\small Atmel AVR Series, Arduino, Raspberry Pi}%{ }{ }%{Software Platforms}{MATLAB, SolidMaple, }
\cvline{OS}{\small Linux (multiple distros/system administration), Windows XP}%{ }{ } 
\cvline{Software}{\small Solidworks, Inkscape, Gimp, GNU Octave, Matlab, Eclipse, KiCad.}
\cvline{Other}{Yarp, Gazebo, \small Motion capture systems : Vicon, xsens MVN.}%{ }{ } 
\cvline{FOSS}{\small Active Contributor to several open source projects such as yarp, iCub, iDynTree, wholeBodyInterface etc. (complete list of recent contributions available at \href{https://github.com/naveenoid}{github}). }


\section{Personal}
\cvline{Birthplace}{\small Chennai, India.}
\cvline{Birth date}{\small $19^{th}$ October, 1983.}
\cvline{Languages}{\small Tamil (Mother tongue), English (Fluent), Hindi (Expert), Korean (Intermediate), German (Intermediate), Italian (Beginner).}
\cvline{Hobbies}{\small Cooking, Volleyball, Comic and Graphic Art, Music (Guitar/Vocals), Hobby Electronics.}


\section{References}
% 
% \begin{enumerate}
\cventry{1}{Giorgio Metta}{Director}{iCub Facility}{Istiuto Italiano di Tecnologia (IIT), Genova, Italy}{Email : \href{mailto:giorgio.metta@iit.it}{giorgio.metta@iit.it}}
\cventry{2}{Francesco Nori}{Team Leader}{Dynamic Interaction Control Lab, iCub Facility}{Istituto Italiano di Tecnologia (IIT), Genova, Italy}{Email : \href{mailto:francesco.nori@iit.it}{francesco.nori@iit.it}}
\cventry{3}{Rolf Pfeifer}{Retd. Professor of Computer Science}{Institute for Informatics}{University of Z\"{u}rich, Switzerland}{Email : \href{mailto:pfeifer@ifi.uzh.ch}{pfeifer@ifi.uzh.ch}}
\cventry{4}{Christopher Harris}{Professor of Neuroscience}{Center for Robotics and Neural Systems}{Plymouth University, United Kingdom}{Email : \href{mailto:chris.harris@plymouth.ac.uk}{chris.harris@plymouth.ac.uk}}


\end{document}


%% end of file `template_en.tex'.
